---
title: "Star Wars Text Mining"
author: "Nick Lechner"
date: "June 17, 2018"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
library(data.table)
library(dplyr)
library(tidyverse)
library(tidytext)
library(stringr)
library(ggplot2)
setwd('~/star_wars_text_mining/')
```

# Text Mining the Star Wars Original Trilogy movie scripts

******

### Importing the data

```{r cars}
e4 = read.table("star-wars-movie-scripts/SW_EPISODEIV.txt", stringsAsFactors = F, header = TRUE, quote = "\"");
colnames(e4) = c('index','character','dialogue')
e4$movie = "a new hope"
e5 = read.table("star-wars-movie-scripts/SW_EPISODEV.txt", stringsAsFactors = F, header = TRUE, quote = "\"")
colnames(e5) = c('index','character','dialogue')
e5$movie = "empire strikes back"
e6 = read.table("star-wars-movie-scripts/SW_EPISODEVI.txt", stringsAsFactors = F, header = TRUE, quote = "\"")
colnames(e6) = c('index','character','dialogue')
e6$movie = "return of the jedi"
```

******

### String Cleaning

```{r}
remove_punctuation = function(df){
  df %>% 
    mutate(dialogue = str_replace_all(dialogue, "[[:punct:]]", "")) %>% 
    mutate(dialogue = tolower(str_replace_all(dialogue, " {2,}", " "))) %>%
    return()
}

create_tidy_text = function(df){
  df %>% 
    unnest_tokens("word", "dialogue") %>% 
    return()
}
```

```{r}
star_wars = list(e4, e5, e6)
star_wars = lapply(star_wars, remove_punctuation)
star_wars = lapply(star_wars, create_tidy_text)
star_wars = do.call(rbind, star_wars)

stop_words_no_punct = stop_words %>% 
  mutate(word = str_replace_all(word, "[[:punct:]]", ""))

star_wars = star_wars %>% anti_join(stop_words_no_punct)
head(star_wars)
```

## Term Frequency By Movie

```{r}
star_wars_words = star_wars %>%
  count(movie, word, sort = TRUE) %>%
  ungroup()

star_wars_words %>% head(20)
```

## TF IDF by movie

Identifies words most unique to each movie

```{r}
star_wars_tfidf = star_wars_words %>% 
  bind_tf_idf(word, movie, n) %>%
  arrange(desc(tf_idf))
star_wars_tfidf %>% head(20)
```

```{r}
 star_wars_tfidf %>% 
  mutate(word  = factor(word, levels = rev(unique(word)))) %>% 
  group_by(movie) %>%
  top_n(12) %>% 
  ggplot(aes(word, tf_idf, fill = movie)) + 
  scale_fill_manual(values = c('#2d54b0', '#ad3a32', '#32ab1d')) +
  geom_col(show.legend =  F) + 
  labs(x = NULL, y = "tf-idf") + 
  facet_wrap(~movie, nrow = 3, scales = "free") + 
  coord_flip()
```

## TF IDF between the 6 main characters in The Empire Strikes Back

Which words are most unique to each character in Episode 5?

```{r}
star_wars %>% 
  filter(movie == "empire strikes back") %>% 
  filter(character %in% c("HAN", "LUKE", "LEIA", "THREEPIO", "VADER", "LANDO")) %>% 
  count(character, word, sort = TRUE) %>% 
  bind_tf_idf(word, character, n) %>%
  arrange(desc(tf_idf)) %>% 
  mutate(word  = factor(word, levels = rev(unique(word)))) %>% 
  group_by(character) %>%
  top_n(8) %>% 
  ggplot(aes(word, tf_idf, fill = character)) + 
  geom_col(show.legend =  F) + 
  labs(x = NULL, y = "tf-idf") + 
  facet_wrap(~character, ncol = 2, scales = "free") + 
  coord_flip() + 
  ggtitle("TF-IDF by character in Empire Strikes Back")
```

## Sentiment Analysis of Darth Vader's Lines in Return of the Jedi

How do Vader's emotions change throughout his lines in return of the Jedi?

```{r}
vader_e5 = e5 %>% 
  remove_punctuation() %>% 
  filter(character == "VADER") %>% 
  mutate(index = row_number()) %>% 
  unnest_tokens("word", "dialogue") %>% 
  anti_join(stop_words_no_punct) %>% 
  inner_join(get_sentiments('nrc')) %>% 
  inner_join(get_sentiments("afinn")) %>% 
  count(index, word, sentiment, score) %>% 
  filter(!(sentiment %in% c('positive', 'negative'))) %>%
  ggplot(aes(index, n*score)) + 
  facet_wrap(~sentiment, scales = "free", ncol = 2) + 
  geom_line(aes(color = as.factor(sentiment))) +
  theme_minimal() + 
  theme(legend.position = "none") + 
  ggtitle("Vader's Feelings by Line in the Empire Strikes Back") + 
  labs(x = "line number", y = "sentiment score")

vader_e6 = e6 %>% 
  remove_punctuation() %>% 
  filter(character == "VADER") %>% 
  mutate(index = row_number()) %>% 
  unnest_tokens("word", "dialogue") %>% 
  anti_join(stop_words_no_punct) %>% 
  inner_join(get_sentiments('nrc')) %>% 
  inner_join(get_sentiments("afinn")) %>% 
  count(index, word, sentiment, score) %>% 
  filter(!(sentiment %in% c('positive', 'negative'))) %>%
  ggplot(aes(index, n*score)) + 
  facet_wrap(~sentiment, scales = "free", ncol = 2) + 
  geom_line(aes(color = as.factor(sentiment))) +
  theme_minimal() + 
  theme(legend.position = "none") + 
  ggtitle("Vader's Feelings by Line in Return of the Jedi") + 
  labs(x = "line number", y = "sentiment score")

vader_e5; vader_e6
```
